Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-11-11 Methods-and-Results.Rmd
typo

\paragraph{Allport's Conditions}We measured how much each of the interactions fulfilled Allport's conditions of optimal contact using a common short scale comprised of four attributes \citep{Islam1993, Voci2003, AlRamiah2012a, Dixon2005}. In particular, we asked participants to rate how much the interaction had equal status ("\textit{The interaction with [name interaction partner] was on equal footing (same status)}"), a common goal ("\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}"), support of authorities ("\textit{The interaction with [name interaction partner] was voluntary}"), and intergroup cooperation ("\textit{The interaction with [name interaction partner] was cooperative}"). We create a mean-averaged index of Allport's conditions in response to past findings indicating that the conditions are best conceptualized jointly and as functioning together rather than as fully independent factors \citep[][, p. 766]{Pettigrew2006}. For full psychometric information see Online Supplementary Material A.

>>>>

\paragraph{Allport's Conditions}We measured how much each of the interactions fulfilled Allport's conditions of optimal contact using a common short scale comprised of four attributes \citep{Islam1993, Voci2003, AlRamiah2012a}. In particular, we asked participants to rate how much the interaction had equal status ("\textit{The interaction with [name interaction partner] was on equal footing (same status)}"), a common goal ("\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}"), support of authorities ("\textit{The interaction with [name interaction partner] was voluntary}"), and intergroup cooperation ("\textit{The interaction with [name interaction partner] was cooperative}"). We create a mean-averaged index of Allport's conditions in response to past findings indicating that the conditions are best conceptualized jointly and as functioning together rather than as fully independent factors \citep[][, p. 766]{Pettigrew2006}. For full psychometric information see Online Supplementary Material A.

### 2022-11-11 Methods-and-Results.tex
typo

We measured how much each of the interactions fulfilled Allport's
conditions of optimal contact using a common short scale comprised of
four attributes \citep{Islam1993, Voci2003, AlRamiah2012a, Dixon2005}.
In particular, we asked participants to rate how much the interaction
had equal status
(``\textit{The interaction with [name interaction partner] was on equal footing (same status)}''),
a common goal
(``\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}''),
support of authorities
(``\textit{The interaction with [name interaction partner] was voluntary}''),
and intergroup cooperation
(``\textit{The interaction with [name interaction partner] was cooperative}'').
We create a mean-averaged index of Allport's conditions in response to
past findings indicating that the conditions are best conceptualized
jointly and as functioning together rather than as fully independent
factors \citep[][, p. 766]{Pettigrew2006}. For full psychometric
information see Online Supplementary Material A.

>>>>

We measured how much each of the interactions fulfilled Allport's
conditions of optimal contact using a common short scale comprised of
four attributes \citep{Islam1993, Voci2003, AlRamiah2012a}. In
particular, we asked participants to rate how much the interaction had
equal status
(``\textit{The interaction with [name interaction partner] was on equal footing (same status)}''),
a common goal
(``\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}''),
support of authorities
(``\textit{The interaction with [name interaction partner] was voluntary}''),
and intergroup cooperation
(``\textit{The interaction with [name interaction partner] was cooperative}'').
We create a mean-averaged index of Allport's conditions in response to
past findings indicating that the conditions are best conceptualized
jointly and as functioning together rather than as fully independent
factors \citep[][, p. 766]{Pettigrew2006}. For full psychometric
information see Online Supplementary Material A.
